Hunting experience shapes individual foraging specialization and predator-prey interactions in an online videogame

### 2023-03-30 manuscript/Chapter2-manuscript.Rmd
integrated some of PO's changes

Authorship statement : With MFF as the leader, all authors participated in conceiving the ideas behind the study. MFF prepared the data, conducted the analyses, and wrote the manuscript. All authors reviewed and accepted the final version of the manuscript.

@@

There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging [@Phillips.etal2017]. This is reflected in the literature showing contrasting results in the links between specialization and fitness. For instance, some studies report increasing benefits of specialization [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015]. This may in part be due to the limited information we have on the ecological contexts favouring specialization over flexibility in nature. However, in predator-prey systems, many studies have outlined that fluctuations in the predictability of prey encounters throughout a predator's lifetime may be a key factor shaping foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018]. The resource-predictability hypothesis argues that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey. In contrast, individual generalists should benefit when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019]. When predators directly interact with their prey, empirical evidence shows that they often match, among other types of traits [see @Kishida.etal2006;@Hanifin.etal2008;@Brousseau.etal2018;@Reimche.etal2020], their locomotor and behavioural traits to those of their prey [@McGhee.etal2013;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022]. Yet, a recurring question that emerges from these studies is whether and how the behavioural adjustments of predators reflect individual differences in experience/learning [@Kelley.Magurran2011]. Thus, uncovering the role of learning in predator-prey systems where interactions are directly monitored would enable researchers to better predict the behavioural decisions and the success of predators when they are hunting.

@@

For each level of experience (i.e. novice, intermediate, advanced), the model estimated the mean speed of every individual (which we call the mean part of the model) and, by using a heterogeneous structure of the residuals, the intra-individual standard deviation of speed for every individual (which we call the dispersion part of the model). Thus, in the mean part of the model, we could estimate among individual differences in the foraging tactic used by predators (i.e. along the slow-fast continuum), while in the dispersion part of the model, we could estimate among individual differences in foraging specialization/flexibility (i.e. intra-individual variability). We followed the same structure for the preys' speed to estimate among individual differences in the mean and standard deviation of speed of the prey groups encountered by predators. For hunting success, we only modeled the mean part of the equation to estimate among individual differences in mean hunting success. For the predator and the prey's speed, we controlled for the average rank of the prey that they encountered as proxy for prey skills on both the mean and dispersion part of the equation. The ranking system in *DBD* was implemented by the company to pair players in a match based on their skill (https://deadbydaylight.fandom.com/wiki/Rank). We used the mean rank of the four prey and applied a square-root transformation. For the predator's hunting success, we controlled for the square-root of the duration of the match.

@@

At the population level, we predicted that predators would become either increasingly flexible or specialized with more experience. However, our results do not support this prediction. Indeed, the observed pattern is more complex given that predators became more flexible with experience at intermediate levels of experience (i.e. intercept of sigma for predator speed is larger for intermediates than novices; Table 2 and Appendix S1: Figure S4), but then return to novice-levels of flexibility with advanced experience (i.e. intercept of sigma for predator speed is smaller for advanced players than intermediates; Table 2 and Appendix S1: Figure S4). Thus, our analyses suggest that population-level behavioural specialization changes nonlinearly (quadratic) with experience rather than linearly.

@@

tab2 <- tab2 %>% 
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. We back-transformed the hunting success values, estimated on a logit scale, back to a probability scale.",
      as_sup("\nb "),
      "The intercept values on the mean part of the equation for all traits indicate average behaviour and success at the population level. The intercept values on the dispersion (i.e. sigma) part of the equation for predator speed indicate behavioural specialization at the population level."
    ),
    ref_symbols = " "
  ) %>%
  font(fontname = "Times New Roman", part = "all") %>%
  width(j = c(2,3,4,5), width = 3.7, unit = "cm") %>%
  width(j = 1, width = 3.2, unit = "cm")

@@

At the individual level, we detected differences in the mean movement speed among predators (i.e. the intercept of the mean speed for the predator ID; Table 3). These differences remained stable to the intermediate stage and then increased at the advanced stage to a level higher than when predators were novice (Table 3 and Appendix S1: Figure S4). For the dispersion part of the model, predators displayed considerable differences in their degree of hunting specialization, and these differences increased with experience (i.e. the intercept of sigma for the predator ID increases with experience; Table 3 and Appendix S1: Figure S4). Thus, the predator population is composed of both specialist and flexible individuals, and they further differentiate themselves as specialist/flexible hunters as they gain experience (Figure 2).

@@

tab3 <- tab3 %>% 
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. All the reported values are standard deviations.",
      as_sup("\nb "),
      "The intercept values on the mean part of the equation for all traits indicate among individual differences in average behaviour and success.",
      as_sup("\nc "),
      "The intercept values on the dispersion (i.e. sigma) part of the equation for predator speed indicate among individual differences in behavioural specialization. For prey speed and hunting success, they indicate among individual differences in the variability of prey encounters and variability in hunting success, respectively."
    ),
    ref_symbols = " "
  ) %>%
  font(fontname = "Times New Roman", part = "all") %>%
  width(j = c(2,3,4,5), width = 3.7, unit = "cm") %>%
  width(j = 1, width = 3.2, unit = "cm")

@@

As we predicted, predators differed in the mean speed of the prey that they encountered across matches. Thus, some individuals encountered prey that were on average slower, while others encountered prey that where on average faster throughout the study period (i.e. the intercept of the mean prey speed for the predator ID; Table 3). These differences were greater when predators reached an advanced level of hunting experience (i.e. the intercept of the mean prey speed for the predator ID was higher at the advanced stage; Table 3 and Appendix S1: Figure S4). In addition, individuals experienced largely distinct degrees of variability among their encounters with the prey. Hence, some predators experienced stable/predictable encounters with their prey, while others experienced unstable/unpredictable encounters with their prey throughout the study period (i.e. the intercept of sigma prey speed for the predator ID; Table 3).

```{r fig2, out.width = "100%", fig.cap = "**Figure 2.** Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility. The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters. Both figure panels are ordered by ascending degree of increase in either specialization or flexibility."}

@@

At all experience levels, predators that were on average faster (mean) also had a lower intra-individual variability (IIV) across their matches (Figure 3 and Appendix S2: Table S1). Thus, faster predators specialized at travelling fast, while slower predators were more flexible in their movement through time. In general, predators that encountered groups of prey that were on average faster (mean) tended to be faster (mean) (Figure 3 and Appendix S2: Table S1). At the three experience levels, there were only weak correlations between predator IIV and mean prey speed (Figure 3 and Appendix S2: Table S1). However, predators that experienced more predictable encounters with their prey (IIV) specialized in a faster hunting tactic (IIV) (Figure 3 and Appendix S2: Table S1). For all the results described above, the correlations strengthen as predators gain experience (Figure 3 and Appendix S2: Table S1).

@@

We did not detect strong correlations between the predators' mean speed and their hunting success (Figure 3 and Appendix S2: Table S1), nor between the predators' IIV in speed and their hunting success (Figure 3 and Appendix S2: Table S1), suggesting that slower/flexible and faster/specialist predators were both equally successful. However, when predators were novice, there was a strong negative correlation between their hunting success and the mean speed of the prey that they encountered (Figure 3 and Appendix S2: Table S1). Hence, novice individuals that encountered faster prey were less successful. This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore (Figure 3 and Appendix S2: Table S1). Thus, the consequences of hunting faster prey were reduced at greater experience levels.

@@

Hunting experience is predicted to increase predator foraging specialization when resources are predictable [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009]. However, when resources vary, others predict that learning with experience should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022]. Our results show that there was no directional increase in either behavioural specialization or flexibility with experience in the population. Instead, the consequences of gaining experience appear to be a property of individuals. We found that each predator developed, through extensive practice, their own expertise and behavioural trajectory, with some specializing in fast-paced hunting, and others adopting a slower and more flexible tactic. The predators' tactics were matched to prey encounters, such that specialized cursorial hunters experienced more predictable encounters, while slower and flexible hunters experienced more unpredictable encounters, with no difference in success between the two predator-types. This predator-prey behavioural matching grew stronger with predator experience, while the strenght of the relationship between hunting success and prey behaviour decreased. Together, our observations suggest that predators in *DBD* adjust their hunting tactic with experience, and the degree to which they specialize in it, to the behaviour of the prey that they encounter throughout their lifetime in the game. Moreover, the predator-prey behavioural escalation through experience suggests that learning may be a catalyst for arms races.

@@

Empirical research in humans and animals shows that task proficiency often increases nonlinearly with experience and stabilizes at an expert level [reviewed in @Dukas2019]. However, we cannot derive conclusions at the individual-level from these studies either because their models assume the same increase in expertise for each individual, or because it is unclear whether their data includes repeated measures of individual success through time. In contrast, our analyses revealed that there was no population increase in expertise over time; instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition. For instance, many predators increased their success (Appendix S1: Figure S1A), but others displayed a decrease in success (Appendix S1: Figure S1B) or no change in success at all with experience. We predicted that this could occur because predators should differ in the type of prey that they encounter, as some may be easier to capture than others. This is often the case in nature as prey can use variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011]. However, prey speed in our study did not shape individual differences in expertise acquisition by predators, even if predators differed in the prey that they encountered. This was unexpected, because prey speed is an important predictor of predator success in this system as well as in others [@Walker.etal2005;@Kelley.Magurran2011;@FraserFranco.etal2022]. Despite that other antipredator tactics may mediate these individual responses by predators, it is likely that individual differences in motivation and perseverance, attention span, or memory retention were also major causes [@Warburton2003;@morand-ferronStudyingEvolutionaryEcology2016;@Dukas2019]. For instance, a persevering predator may increase its success much more steadily than an unmotivated predator that quickly abandons a chase. Another factor that may explain differences in the development of expertise is the time delay between hunting events. For example, a predator that played 300 matches in the span of six months might forget more critical information (e.g. prey escape patterns or muscle memory) than one that played 300 matches in the span of 6 days. While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between success and experience [@Endler1991;@Wright.etal2022].

@@

The predator population displayed an increase in foraging flexibility when reaching the intermediate level of experience. As it reached an advanced level of experience, it returned to a level of flexibility that was similar to novice levels. This is commonly observed in juvenile predators across the animal kingdom, because exploring and learning different tactics at this developmental stage is crucial to become a skillful hunter [@Vehanen2003;@Johnson.Wilbrecht2011;@Thiers.etal2014;@deGrissac.etal2016]. Thus, the predators in *DBD* were probably exploring and refining different tactics at this stage of experience. Interestingly, differences in individual foraging specialization among players increased with experience, which was related to the degree of variability in prey encounters. Predators that experienced predictable encounters with their prey across matches specialized in hunting at high speeds, while those that experienced less predictable encounters adopted a slower and flexible strategy. This is similar to other studies finding that fast-paced hunting is a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018;@Szopa-Comley.Ioannou2022]. On the contrary, instead of focusing solely on one tactic, predators that experienced unpredictable encounters probably adjusted their behaviour to minimize the consequences of uncertainty. Importantly, 13% of the predator population displayed the greatest change in foraging specialization/flexibility with experience (i.e. $\ge$ 0.2 change in standard deviation), 56% displayed lower changes (i.e. >0.05 and <0.2 change in standard deviation), while 43% remained relatively stable (i.e. $\le$ 0.05 change in standard deviation). Thus, while individual differences in specialization did increase with experience, they were in part driven by a proportion of the population that displayed greater changes in behaviour compared to others.

>>>>

Authorship statement : With MFF as the leader, all authors participated in conceiving the ideas behind the study. MFF prepared the data, conducted the analyses, and wrote the manuscript with input from all coauthors. All authors reviewed and accepted the final version of the manuscript.

@@

There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging [@Phillips.etal2017]. This is reflected in the literature showing contrasting results in the links between specialization and fitness. For instance, some studies report increasing benefits of specialization [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015]. This may in part be due to the limited information we have on the ecological contexts favouring specialization over flexibility in nature. However, in predator-prey systems, many studies have outlined that fluctuations in the predictability of prey encounters throughout a predator's lifetime may be a key factor shaping foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018]. The resource-predictability (or resource-heterogeneity) hypothesis argues that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey. In contrast, individual generalists should benefit when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019]. When predator-prey interactions are directly observed, empirical evidence shows that predators often match, among other types of traits [see @Kishida.etal2006;@Hanifin.etal2008;@Brousseau.etal2018;@Reimche.etal2020], their locomotor and behavioural traits to those of their prey [@McGhee.etal2013;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022]. Yet, a recurring question that emerges from these studies is whether and how the behavioural adjustments of predators reflect individual differences in experience/learning [@Kelley.Magurran2011]. Thus, uncovering the role of learning in predator-prey systems where interactions are directly monitored would enable researchers to better predict the behavioural decisions and the success of predators when they are hunting.

@@

For each level of experience (i.e. novice, intermediate, advanced), the model estimated the mean speed of every individual (which we call the mean part of the model) and, by using a heterogeneous structure of the residuals, the intra-individual standard deviation of speed for every individual (which we call the dispersion part of the model). Thus, in the mean part of the model, we could estimate among individual differences in the foraging tactic used by predators (i.e. along the slow-fast continuum), while in the dispersion part of the model, we could estimate among individual differences in foraging specialization/flexibility (i.e. intra-individual variability). We followed the same structure for the preys' speed to estimate among individual differences in the mean and standard deviation of speed of the prey groups encountered by predators. For the mean part of the model, it allows us to test whether individual predators differed in the average speed of the groups of prey encountered across the study. For the dispersion part, it allows us to test whether individual predators differed in the (dis)similarity of the groups of prey encountered across the study (i.e. if resource heterogeneity was higher for some individuals compared to others). For hunting success, we only modeled the mean part of the equation to estimate among individual differences in mean prey capture. For the predator and the prey's speed, we controlled for the average rank of the prey that they encountered as proxy for prey skills on both the mean and dispersion part of the equation. The ranking system in *DBD* was implemented by the company to pair players in a match based on their skill (https://deadbydaylight.fandom.com/wiki/Rank). We used the mean rank of the four prey and applied a square-root transformation. For the predator's hunting success, we controlled for the square-root of the duration of the match.

@@

At the population level, predators did not change their mean speed with experience (i.e. intercept of the mean predator speed; Table 2). Moreover, there was no directional increase in foraging flexibility or specialization with experience. Indeed, the observed pattern is more complex given that predators became more flexible with experience at intermediate levels of experience (i.e. intercept of sigma for predator speed is larger for intermediates than novices; Table 2 and Appendix S1: Figure S4), but then return to novice-levels of flexibility with advanced experience (i.e. intercept of sigma for predator speed is smaller for advanced players than intermediates; Table 2 and Appendix S1: Figure S4). Thus, our analyses suggest that population-level behavioural specialization changes nonlinearly (quadratic) with experience rather than linearly.

@@

tab2 <- tab2 %>% 
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. We back-transformed the hunting success values, estimated on a logit scale, back to a probability scale.",
      as_sup("\nb "),
      "The intercept values on the mean part of the equation for all traits indicate mean behaviour and success at the population level. The intercept values on the dispersion (i.e. sigma) part of the equation for predator speed indicate behavioural specialization at the population level."
    ),
    ref_symbols = " "
  ) %>%
  font(fontname = "Times New Roman", part = "all") %>%
  width(j = c(2,3,4,5), width = 3.7, unit = "cm") %>%
  width(j = 1, width = 3.2, unit = "cm")

@@

At the individual level, we detected differences in the mean movement speed among predators (i.e. the intercept of the mean speed for the predator ID; Table 3). These differences remained stable from the novice to the intermediate stages, and then increased at the advanced stage to reach a level higher than when predators were novice (Table 3 and Appendix S1: Figure S4). Predators displayed considerable differences in their degree of hunting specialization, and these differences increased with experience (i.e. the intercept of sigma for the predator ID increases with experience; Table 3 and Appendix S1: Figure S4). Thus, as individual predators gain experience, the population becomes more heterogeneous, with an assemblage of both specialist and flexible hunters. Moreover, some individual predators switched from a flexible to a specialized hunting tactic, and vice-versa, as they gained experience (Figure 2). Importantly, 13% of the predator population displayed a large change in foraging specialization/flexibility with experience (i.e. $\ge$0.2 change in standard deviation), 56% displayed lower changes (i.e. >0.05 and <0.2 change in standard deviation), while 43% remained relatively stable (i.e. $\le$0.05 change in standard deviation).

@@

tab3 <- tab3 %>% 
  footnote(
    i = 1, j = 1,
    part = "header",
    value = as_paragraph(
      as_sup("a "),
      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. All the reported values are standard deviations.",
      as_sup("\nb "),
      "The intercept values on the mean part of the equation for all traits indicate among individual differences in mean behaviour and success.",
      as_sup("\nc "),
      "The intercept values on the dispersion (i.e. sigma) part of the equation for predator speed indicate among individual differences in behavioural specialization. For prey speed and hunting success, they indicate among individual differences in the variability of prey encounters and variability in hunting success, respectively."
    ),
    ref_symbols = " "
  ) %>%
  font(fontname = "Times New Roman", part = "all") %>%
  width(j = c(2,3,4,5), width = 3.7, unit = "cm") %>%
  width(j = 1, width = 3.2, unit = "cm")

@@

As we predicted, predators differed in the mean speed of the prey that they encountered across matches. Thus, some individuals encountered prey that were on average slower, while others encountered prey that where on average faster throughout the study period (i.e. the intercept of the mean prey speed for the predator ID; Table 3). These differences were greater when predators reached an advanced level of hunting experience (i.e. the intercept of the mean prey speed for the predator ID was higher at the advanced stage; Table 3 and Appendix S1: Figure S4). In addition, individuals differed in the heterogeneity of the groups of prey encountered across the study period. Hence, some predators encountered prey groups with similar average speeds, while others encountered prey groups with different average speeds throughout the study period (i.e. the intercept of sigma prey speed for the predator ID; Table 3).

```{r fig2, out.width = "100%", fig.cap = "**Figure 2.** Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility. The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters. Both figure panels are ordered by ascending degree of increase in either specialization or flexibility. We selected the individuals displayed in the figure by first substracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selecting those with the greatest difference using the 25% and 75% quantiles. Individuals on panel A have an increase in specialization $\ge$0.2 standard deviations, while those on panel B have an increase in flexibility $\ge$"0.28 standard deviations.}

@@

At all experience levels, predators that were on average faster (mean) also had a lower intra-individual variability (IIV; Figure 3 and Appendix S2: Table S1). Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement through time. Predators that were on average faster (mean) also encountered groups of prey that were on average faster (mean) (Figure 3 and Appendix S2: Table S1). At the three experience levels, there were only weak correlations between IIV in predator speed and mean prey speed (Figure 3 and Appendix S2: Table S1). However, predators that encountered groups of prey with similar speeds (IIV) specialized in their hunting tactic (IIV) (Figure 3 and Appendix S2: Table S1). Hence, predators that encountered groups of prey with similar average speeds were more specialized, while those that encountered groups of prey with different average speeds were more flexible. For all the results described above, the correlations strengthen as predators gain experience (Figure 3 and Appendix S2: Table S1).

@@

We did not detect strong correlations between the predators' mean speed and their hunting success (Figure 3 and Appendix S2: Table S1), nor between the predators' IIV in speed and their hunting success (Figure 3 and Appendix S2: Table S1), suggesting that slower/flexible and faster/specialist predators were both equally successful. However, novice individuals that encountered groups of prey with faster speeds were less successful (Figure 3 and Appendix S2: Table S1). This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore (Figure 3 and Appendix S2: Table S1). Thus, the consequences of hunting faster prey were reduced at greater experience levels.

@@

Hunting experience is predicted to increase predator foraging specialization when resources are predictable [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009]. However, when resources vary, others predict that learning with experience should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022]. Our results show that there was no directional increase in either behavioural specialization or flexibility with experience in the population. Instead, both mechanisms operated simultaneously, such that each individual predator developed their own expertise and behavioural trajectory over successive encounters with prey; some specialized in fast-paced hunting, and others adopted a slower and more flexible tactic. The predators' tactics were matched to speed of the prey that they encountered, such that specialized cursorial hunters encountered similar groups of prey, while slower and flexible hunters encountered varying groups of prey, with no difference in success between the two types of hunters. This predator-prey behavioural matching grew stronger with predator experience, while the strenght of the relationship between the predator's hunting success and prey behaviour decreased. Together, our observations suggest that predators in *DBD* learn to adjust their hunting tactic to the behaviour of the prey that they encounter throughout their lifetime in the game. Moreover, the predator-prey behavioural escalation through experience suggests that learning may be a catalyst for arms races.

@@

Empirical research in humans and animals shows that task proficiency often increases nonlinearly with experience and stabilizes at an expert level [reviewed in @Dukas2019]. However, we cannot derive conclusions at the individual-level from these studies either because their models assume the same increase in expertise for each individual, or because it is unclear whether their data includes repeated measures of individual success through time. In contrast, our analyses revealed that there was no population increase in expertise over time; instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition. Many predators increased their success (Appendix S1: Figure S1A), but others displayed a decrease in success (Appendix S1: Figure S1B) or no change in success at all with experience. We predicted that this could occur because predators could differ in the prey that they encounter by chance, as some may be easier and others more difficult to capture. In nature, prey can use a variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011]. In *DBD* we showed in a previous study that faster speed and space coverage is an effective antipredator strategy used by the prey [@FraserFranco.etal2022]. Other studies also show that faster escapes are effective to escape predation [@Walker.etal2005;@Kelley.Magurran2011;Martin.etal2022]. Yet, prey speed in our current study did not shape individual differences in expertise acquisition by predators, even if predators differed in the prey that they encountered. It is however possible that other antipredator tactics mediated these individual predator responses, as we focused solely on prey speed at the group level. For example, unpredictable escapes and turning angles are important locomotor traits enabling prey to confuse human and non-human predators during the attack sequence [@Jones.etal2011;@Briffa2013;@Herbert-Read.etal2017;@Moore.etal2017;@Richardson.etal2018], which could prove to be difficult for a predator to learn and adjust to if it more often encountered prey using these tactics.

Alternatively, it is possible that individual differences in learning were also major causes, irrespective of differences in prey encounters [@Warburton2003;@morand-ferronStudyingEvolutionaryEcology2016;@Dukas2019]. *ici je pourrais plutot parler de différences d'apprentissage. Il pourrait même être + difficile d'apprendre à capturer des proies selon leur comportement car ça ne donne pas toujours autant de signaux directs que la coloration par exemple. Trouver des sources pour la coloration...ajouter que c'est irrespective of prey behaviour pour différencier par rapport à l'explication d'en haut*

 For instance, a persevering predator may increase its success much more steadily than an unmotivated predator that quickly abandons a chase. Another factor that may explain differences in the development of expertise is the time delay between hunting events. For example, a predator that played 300 matches in the span of six months might forget more critical information (e.g. prey escape patterns or muscle memory) than one that played 300 matches in the span of 6 days.

 While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between success and experience [@Endler1991;@Wright.etal2022].

@@

The predator population displayed an increase in foraging flexibility when reaching the intermediate level of experience. As it reached an advanced level of experience, it returned to a level of flexibility that was similar to novice levels. This is commonly observed in juvenile predators across the animal kingdom, because exploring and learning different tactics at this developmental stage is crucial to become a skillful hunter [@Vehanen2003;@Johnson.Wilbrecht2011;@Thiers.etal2014;@deGrissac.etal2016]. Thus, the predators in *DBD* were probably exploring and refining different tactics at this stage of experience. Interestingly, differences in individual foraging specialization among players increased with experience, which was related to the degree of variability in prey encounters. Predators that experienced predictable encounters with their prey across matches specialized in hunting at high speeds, while those that experienced less predictable encounters adopted a slower and flexible strategy. This is similar to other studies finding that fast-paced hunting is a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018;@Szopa-Comley.Ioannou2022]. On the contrary, instead of focusing solely on one tactic, predators that experienced unpredictable encounters probably adjusted their behaviour to minimize the consequences of uncertainty.

ici une phrase qui rappelle que pas tout le monde a appris
 Thus, while individual differences in specialization did increase with experience, they were in part driven by a proportion of the population that displayed greater changes in behaviour compared to others.
